Network Configuration Synthesis with Abstract Topologies

### 2016-11-15 paper/abstraction/paper.tex
fix references. fix spelling mistakes

As described earlier (\S\ref{sec:introduction}), templates are hard to author and hard to validate. Worse, templates that work for one topology may not work for seemingly-inconsequential variations (which may arise after the network evolves).
Consider the network in Figure~\ref{fig:example2}, which is similar to Figure~\ref{fig:example}: it has the same five roles, connected in a similar hierarchy. One might think that the same templates (with different database entries) can be used for both cases. However, if the templates are configured to disallow ``valley" paths (per policy (5) above), they will work for Figure~\ref{fig:example} but silently violate the fault tolerance policy $(8)$ when used for Figure~\ref{fig:example2}.  Specifically, in Figure~\ref{fig:example2}, an aggregation-based blackhole (\S\ref{sec:background}) will occur when the link S1--A1 fails; after this failure, S1 has no valley-free path to P[1--2] even though it will continue to get traffic for these prefixes as it announces the covering prefix PG (because it gets routes for P[3--4]). No such blackhole will occur in Figure~\ref{fig:example} after a single link failure because spine routers have two links to each pod.

@@

More specifically, a network topology is a graph $G$ = ($V, E$), which consists of a set of vertices $V$ and a set of directed edges $E \colon V \times V$. A role-based abstraction is a graph homomorphism from $G$ to an abstract graph $G^A$ = ($V^A$,$E^A$). A graph homomorphism $f : G \rightarrow G^A$ maps each node in the concrete graph to a node in the abstract graph such that, whenever $(u,v) \in E$, then $(f(u),f(v)) \in E^A$. The role-based abstraction therefore overapproximates the connectivity of the underlying concrete graphs.

@@

      Fattree~\cite{fattree} & -- & \cmark & \cmark & \cmark & \cmark  \\ \hline
      Facebook~\cite{facebook-fattree} & -- & \cmark & \cmark & \cmark & \cmark \\ \hline
      F10~\cite{f10-fattree} & -- & \cmark & \cmark & \cmark & \cmark \\ \hline
      VL2~\cite{vl2-fattree} & -- & \cmark & \cmark & \cmark & \cmark \\ \hline
%      \end{tabular}
%  \end{center}
%  \vspace{-.6em}
%  \caption{Expressiveness and analysis precision for fat tree topologies with valley-free routing policy.}
%  \label{fig:analysis-precision2}
%\end{figure}
%
%\begin{figure}[t!]
%  \begin{center}
%      \begin{tabular}{| l | c | c | c | c | c | }
%      \hline
%      \textbf{Topology} & \textbf{Fixed} & \multicolumn{2}{|c|}{\textbf{Reachability}} & \multicolumn{2}{|c|}{\textbf{K-paths}} \\ \hline
%      & & Some & All & Some & All \\
%      & & Pairs & Pairs & Pairs & Pairs \\ \hline

@@

      Fattree~\cite{fattree} & -- & \cmark & \cmark & \cmark & \Conserv  \\ \hline
      Facebook~\cite{facebook-fattree} & -- & \cmark & \cmark & \cmark & \cmark \\ \hline
      F10~\cite{f10-fattree} & -- & \cmark & \cmark & \cmark & \Conserv \\ \hline
      VL2~\cite{vl2-fattree} & -- & \cmark & \cmark & \cmark & \Conserv \\ \hline
      BCube~\cite{bcube} & $k$ & \cmark & \cmark & \Conserv & \Conserv \\ \hline
      DCell~\cite{dcell} & $k$ & \cmark & \cmark & \Conserv & \Conserv \\ \hline
         %& HCN & $h$ & \cmark & \xmark \\
      Butterfly~\cite{butterfly} & $n$ & \cmark & \cmark & \cmark & \cmark \\ \hline
      Hypercube & $N$ & \cmark & \cmark & \cmark & \cmark \\ \hline
      HyperX~\cite{hyperx} & $L$ & \cmark & \cmark & \cmark & \cmark \\ \hline
      \end{tabular}
  \end{center}
  \vspace{-.6em}
  \caption{Expressiveness and precision of \sysname.}
  \label{fig:analysis-precision}
  %\vspace{-1em}
\end{figure}

@@

\para{Network verification}
A complementary approach to reducing configuration errors is by analyzing the forwarding rules or the configuration of a network to ensure the absence of (a class of) bugs~\cite{anteater,hsa,veriflow,feamster+:rcc,ipassure,batfish,bagpipe,arc,era,surgery}. Our focus, in contrast, is on a correct-by-construction approach. It has the downside that operators must learn to express policies in a new language, but it saves them from the challenging and time-consuming task of manual configuration generation.

>>>>

As described earlier (\S\ref{sec:introduction}), templates are hard to author and hard to validate. Worse, templates that work for one topology may not work for seemingly-inconsequential variations (which may arise after the network evolves).
Consider the network in Figure~\ref{fig:example2}, which is similar to Figure~\ref{fig:example}: it has the same five roles, connected in a similar hierarchy. One might think that the same templates (with different database entries) can be used for both cases. However, if the templates are configured to disallow ``valley" paths (per policy (5) above), they will work for Figure~\ref{fig:example} but silently violate the fault tolerance policy $(8)$ when used for Figure~\ref{fig:example2}.  Specifically, in Figure~\ref{fig:example2}, an aggregation-based black hole (\S\ref{sec:background}) will occur when the link S1--A1 fails; after this failure, S1 has no valley-free path to P[1--2] even though it will continue to get traffic for these prefixes as it announces the covering prefix PG (because it gets routes for P[3--4]). No such black hole will occur in Figure~\ref{fig:example} after a single link failure because spine routers have two links to each pod.

@@

More specifically, a network topology is a graph $G$ = ($V, E$), which consists of a set of vertices $V$ and a set of directed edges $E \colon V \times V$. A role-based abstraction is a graph homomorphism from $G$ to an abstract graph $G^A$ = ($V^A$,$E^A$). A graph homomorphism $f : G \rightarrow G^A$ maps each node in the concrete graph to a node in the abstract graph such that, whenever $(u,v) \in E$, then $(f(u),f(v)) \in E^A$. The role-based abstraction therefore over-approximates the connectivity of the underlying concrete graphs.

@@

      Fat tree~\cite{fattree} & -- & \cmark & \cmark & \cmark & \cmark  \\ \hline
      Facebook~\cite{facebook-fattree} & -- & \cmark & \cmark & \cmark & \cmark \\ \hline
      F10~\cite{f10-fattree} & -- & \cmark & \cmark & \cmark & \cmark \\ \hline
      VL2~\cite{vl2-fattree} & -- & \cmark & \cmark & \cmark & \cmark \\ \hline
%      \end{tabular}
%  \end{center}
%  \vspace{-.6em}
%  \caption{Expressiveness and analysis precision for fat tree topologies with valley-free routing policy.}
%  \label{fig:analysis-precision2}
%\end{figure}
%
%\begin{figure}[t!]
%  \begin{center}
%      \begin{tabular}{| l | c | c | c | c | c | }
%      \hline
%      \textbf{Topology} & \textbf{Fixed} & \multicolumn{2}{|c|}{\textbf{Reachability}} & \multicolumn{2}{|c|}{\textbf{K-paths}} \\ \hline
%      & & Some & All & Some & All \\
%      & & Pairs & Pairs & Pairs & Pairs \\ \hline

@@

      Fat tree~\cite{fattree} & -- & \cmark & \cmark & \cmark & \Conserv  \\ \hline
      Facebook~\cite{facebook-fattree} & -- & \cmark & \cmark & \cmark & \cmark \\ \hline
      F10~\cite{f10-fattree} & -- & \cmark & \cmark & \cmark & \Conserv \\ \hline
      VL2~\cite{vl2-fattree} & -- & \cmark & \cmark & \cmark & \Conserv \\ \hline
      BCube~\cite{bcube} & $k$ & \cmark & \cmark & \Conserv & \Conserv \\ \hline
      DCell~\cite{dcell} & $k$ & \cmark & \cmark & \Conserv & \Conserv \\ \hline
         %& HCN & $h$ & \cmark & \xmark \\
      Butterfly~\cite{butterfly} & $n$ & \cmark & \cmark & \cmark & \cmark \\ \hline
      Hypercube & $N$ & \cmark & \cmark & \cmark & \cmark \\ \hline
      HyperX~\cite{hyperx} & $L$ & \cmark & \cmark & \cmark & \cmark \\ \hline
      \end{tabular}
  \end{center}
  \vspace{-.6em}
  \caption{Expressiveness and precision of \sysname.}
  \label{fig:analysis-precision}
  %\vspace{-1em}
\end{figure}

@@

\para{Network verification}
A complementary approach to reducing configuration errors is to analyze the forwarding rules or the configuration of a network to ensure the absence of (a class of) bugs~\cite{anteater,hsa,veriflow,feamster+:rcc,ipassure,batfish,bagpipe,arc,era,surgery}. Our focus, in contrast, is on a correct-by-construction approach. It has the downside that operators must express policies in a new language, but it saves them from the challenging and time-consuming task of manual configuration generation.
